Quantum Hoare Type Theory

### 2020-06-08 ms-paper/ms-paper.tex
Add verification steps for first two examples

In this section, we show some simple examples from the QIO work~\cite{qio} translated in our language and annotated with their program specifications using their Quantum Hoare types. An observation is that translating the programs was a very simple process except for coming up with the right specifications for the programs. We take some liberty in writing our typeset syntax as plain text for convenience and provide some commentary on assertions specified for these programs.

@@

\subsubsection*{Hello Quantum World}
\leavevmode

\textbf{Code:}

@@

\textbf{Verification steps:}

@@

\subsubsection*{Coin Toss}
\leavevmode

@@

\subsubsection*{Testing Bell Pair}
\leavevmode
\todo{TODO: Should the type be \type{Bool} $\otimes$ \type{Bool}?}

>>>>

In this section, we show some simple examples from the QIO work~\cite{qio} translated in our language and annotated with their program specifications using their Quantum Hoare types. An observation is that translating the programs was a very simple process except for coming up with the right specifications for the programs. We provide some commentary on assertions specified for these programs.

@@

\subsubsection{Hello Quantum World}
\leavevmode

@@

Verification steps follow:

@@

\subsubsection{Coin Toss}
\leavevmode

@@

Verification steps follow:

\begin{minipage}{0.95\linewidth}
\begin{lstlisting}[language=QHaskell]
rnd : {emp} r : Bool {emp}
-- P0: emp
    = do q <= mkQbit false;
-- P1: P0 \o (q |-> |0\>)
         applyU (H q);
-- P2: P1 \o ((q |-> |0\>) -o (q |-> |+\>))
         measQbit q
-- P3: P2 \o ((q |-> -) -o emp)
\end{lstlisting}
\end{minipage}

\subsubsection{Testing Bell Pair}
\leavevmode
\todo{TODO: Should the type be \type{Bool} $\otimes$ \type{Bool}?}
